Estimate RSV onset and peak timing

### 2023-01-11 RSV_timing_explain/RSV_timing_tutorial.Rmd
add peak timing calculation

$$X_t=\mu+R\cos(2\pi ft+d)+e_t$$
Where 
\
$X_t$ is the time-series contains a periodic (cyclic) component.
\
$\mu$ is mean of the series.
\
$R$ is the amplitude of seasonality.
\
$f=\frac{1}{period}$ is the frequency of the periodic.
\
$d$ is the phase or horizontal offset.
\
$e_t$ is the random error (noise) of the series.
\
$t$ is the time step

@@

#other series shifted by 2 months
xt2a=amp2*cos(2*3.14159*t*freq+1)

@@

>>>>

$$X_t=\mu+R\cos(2\pi ft-d)+e_t$$
Where 
\
$X_t$ is the time-series contains a periodic (cyclic) component.
\
$\mu$ is mean of the series.
\
$R$ is the amplitude of seasonality.
\
$f=\frac{1}{period}$ is the frequency of the periodic.
\
$d$ is the phase or horizontal offset.
\
$e_t$ is the random error (noise) of the series.
\
$t$ is the time step

@@

#other series shifted by 2 months
xt2a=amp2*cos(2*3.14159*t*freq-1)

@@

## Calculate phase of the 12 month period in state1 and state2

```{r}
# Phase angle
phase12_xt1 <- -atan(beta_sin12_xt1/beta_cos12_xt1)
phase12_xt1
# True value = 0
phase12_xt2 <- -atan(beta_sin12_xt2/beta_cos12_xt2)
phase12_xt2
# True value = 1
```

## Calculate peak timing in month in state1 and state2

```{r}
# Average peak timing
12*(1-phase12_xt1/(2*pi)) # True value = 0 month 
12*(1-phase12_xt2/(2*pi)) # True value = 2 month
```
**Note: the period is 12 month** 
- Therefore, peak timing of 12.06 month (year 1) equal to peak timing of 0.06 month (year 0)
\
\
- peak timing of 13.93 month (year 1) equals to 1.93 month (year 0)
